\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage[margin=1.5cm]{geometry}
\usepackage[english]{babel}
\usepackage{array,xcolor}
\usepackage{hyperref}
\usepackage{multicol}

\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.20\textwidth}}
\newcolumntype{R}{p{0.80\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

\setlength{\parindent}{0pt}
\pagenumbering{gobble}

\title{\vspace{-1.5em}Jacob Errington}
\author{\texttt{jake@mail.jerrington.me}}
\date{}

\begin{document}

\maketitle

\begin{multicols}{2}
    \centering
    \begin{tabular}{r l}
        Address & 1105 rue Woodland \\
              ~ & Verdun, H4H 1W1   \\
              ~ & Quebec
    \end{tabular}
    \columnbreak
    \begin{tabular}{r l}
        Nationality & Canadian \\
        Date of birth & 10 January 1995 \\
        Phone & +1 514 503-3100
    \end{tabular}
\end{multicols}

\hrule

\subsection*{Work experience}

\begin{tabular}[h]{L!{\VRule}R}
    Jan. 2015 to Sept. 2015
        & CTO \& Cofounder, full-stack web development, native Android development                                       \\
        & Ahvoda Recruitment Inc., \url{http://ahvoda.com/}                                                              \\
        & \emph{Participated in McGill's X-1 Accelerator program}, \url{http://mcgillx1accelerator.com}                  \\
    Jun. 2014 to Jun. 2015
        & Research assistant, scientific programming in genetics, big data                                               \\
        & McGill University and Genome Qu\'ebec Innovation Centre                                                        \\
        & 740 Avenue du Dr Penfield, Montreal, Qu\'ebec                                                                  \\
        & Supervised by \href{http://simongravel.lab.mcgill.ca/Home.html}{Simon Gravel}, \texttt{simon.gravel@mcgill.ca}
\end{tabular}

\subsection*{Education}

\begin{tabular}[h]{L!{\VRule}R}
    2014-2017 & B.Sc. Comp. Sci. \& Math., McGill University, Montreal.                              \\
              & CGPA $3.62$                                                                          \\
    2012-2014 & D\'EC in Pure and Applied Science (First Choice profile), Dawson College, Westmount. \\
              & Admitted to the Honour Roll every semester; Final overall average above 90\%.
\end{tabular}

\subsection*{Projects}

\begin{description}
    \item[CBKB.] \emph{Crystalball Knife Bomb} is the reference implementation
        of a compiler for an all-emoji esoteric functional programming language
        that my team and I designed at MHacks, Fall 2015. \\
        \url{http://github.com/labcoders/crystalball-knife-bomb}
    \item[HackSignal.] At hackathons, it can be hard to find the mentors that
        you need when you get stuck. HackSignal is an online platform for peer
        mentorship at hackathons that emphasizes real-life interaction between
        the mentor and mentee. A rewrite of the webapp into Haskell from Python
        is in progress. \\
        \url{http://github.com/djeik/hacksignal}~
        \url{http://github.com/djeik/hacksignal-naph}
    \item[FishBucketChallenge.] To help scientists working on medication for
        ALS (Lou Gehrig's disease), in 24 hours my team developed computer
        vision software in Python to track the movement of zebra fish, and
        determine their maximum velocity based only on low-resolution grayscale
        videos of the fish. \\
        \url{https://github.com/ndejay/fish-bucket-challenge}
    \item[Vent/Tea.] Online platform to match people who need someone to talk
        to with trained listeners. The pairs of people meet up physically over
        tea or coffee to talk, rather than simply discuss through an online
        chat. \\
        \url{http://github.com/ventovertea/ventovertea}~
        \url{http://ventovertea.com/}
    \item[TeXnote.] Online environment for creating documents in \LaTeX.
        Document source code is written directly into the browser, and a live
        PDF preview is displayed to the side. The code is compiled server-side,
        so no client installation is needed. The SendGrid API is integrated to
        allow users to easily include scanned images into their documents to
        facilitate rapid document drafting. Built at MHacks, Winter 2015. \\
        \emph{Winner of the SendGrid API prize.} \\
        \url{https://github.com/labcoders/texnote}
\end{description}

\subsection*{Volunteer \& Outreach}

\begin{tabular}[h]{L!{\VRule}R}
    Sept. 2015 to \emph{present}
        & Outreach director at HackMcGill ~ \url{http://hackmcgill.com} \\
        & Organize community events, participate in organizing McHacks
\end{tabular}

\end{document}
